---
title: "Week 3"
subtitle: "Survey design"
author: "Dani Cosme"
output:
  xaringan::moon_reader:
    css: ["default", "css/dcos.css", "css/dcos-fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: atelier-lakeside-light
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300,
  fig.align = "center", out.width = "80%", cache = FALSE)

if(!require('tidyverse')) {
	install.packages('tidyverse')
}
if(!require('devtools')) {
	install.packages('devtools') 
}
if(!require('emo')) {
	devtools::install_github("hadley/emo")
}
if(!require('xaringanExtra')) {
	devtools::install_github("gadenbuie/xaringanExtra")
}
if(!require('countdown')) {
	devtools::install_github("gadenbuie/countdown")
}
```

## Check-in

### Assignment

* Emphasize social norms and Penn identity
--

* Draft is [here](https://docs.google.com/document/d/14jWABXCFx-ydFAtiAWmlEZFJdpu6RtDPnvWlaTJAn3s/edit?usp=sharing)

--

* Plan

--

  * Finish creating the draft (by Monday March 22)

--

  * Give feedback, keeping [your critiques](https://jamboard.google.com/d/1iASnxsICB9oHyaCSPYAGAxukEeMkdV-TEeNUnO37l1g/edit?usp=sharing) of the fall emails in mind (by Friday March 26)

--
  
  * Randomize emails to the experimental or control condition and send (April 19)

---

## Check-in

### Prework

  `r emo::ji("check")` Complete CITI certificate (deadline Monday March 22)
  
  `r emo::ji("check")` Download [R](https://cran.r-project.org/) and [RStudio](https://rstudio.com/products/rstudio/download/)
  
  `r emo::ji("check")` Complete [R Bootcamp modules](https://dcosme.github.io/pltv-seminar/prework/) (by March 26) & post questions to Slack

---
class: center, middle

## Goal for this week

Collectively design a survey<br><br>

---
## Common issues / sources of bias
### Questions

--

* <b>Leading</b> questions

--

  * How much do you love being in this seminar?

--

* <b>Loaded</b> questions

--

  * How much did you like drafting the message framing text?

--

* <b>Double-barreled</b> questions

--

  * How excited are you to draft and give feedback on the survey?

--

* <b>Social desirability</b>

--

  * How good is Dani at teaching?

---
## Common issues / sources of bias
### Responses

--

* Missing options

--

  * How much do you love being in this seminar?
  
  * Completely love / Completely hate

--

* Incorrect scale anchors

--

  * How much do you love being in this seminar?
  
  * Strongly disagree --> Agree

---
## Critique

```{r, echo = FALSE}
countdown::countdown(minutes = 5, seconds = 00, font_size = "2em")
```

Let's critique [this survey](https://action.donaldjtrump.com/post-2020-rnc-approval-poll) and identify sources of bias. 

Use [this doc](https://docs.google.com/document/d/1IWz8yMpfE1-THtswQhQvcxxBUbIKDgwJDMId2u8yks4/edit?usp=sharing) to annotate the survey items together.


---
## PLTV survey components

--

* Description of the survey, consent, compensation

--

* Screening

--

* Message framing experiment
  * Within- versus between-person design
  * Manipulation checks
  * Issues related to power

--

* Dependent variables
  * Depends on design

--

* Moderator / individual difference measures

--

* Open-ended questions

--

* Student status and demographics

--

* Debrief


---
## Brainstorming

```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### Experimental manipulation

.can-edit.key-likes[
- Messages content
  - 
  
- Message framing
  - 
  
]

---
## Brainstorming

```{r xaringan-editable2, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### Dependent variables

.can-edit.key-likes[
- Message-level
  - Relevance, motivation, sharing, manipulation checks
  
- Person-level
  - Social norms, Penn identity strength
  - Voting attitudes, intentions
  
]

---
## Brainstorming

```{r xaringan-editable3, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### Individual difference measures

.can-edit.key-likes[
- Motivation, civic engagement attitudes, political efficacy

]

---
## Brainstorming

```{r xaringan-editable4, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

### Other measures

.can-edit.key-likes[
- Reasons for voting/not voting
- Open-ended: Advantages/disadvantages/barriers/solutions to voting

]

---
## Design considerations

--

* Survey flow / order of measures

--

* Display logic

--

* Randomization (items and measures)

--

* Forced or requested responses

--

* Page breaks

--

* Embedded data and unique links

--

* Item names

--

* Automatically generated values

--

* Analysis plan


---
## Assignment
Design a survey based on our research question.

--

1. Form drafting and feedback teams

--

2. Drafting team: Create stimuli for the experimental component and modify the survey by **March 26**

--

3. Feedback team: Provide feedback on the drafting team's survey [in this doc](https://docs.google.com/document/d/1H1_B-Mrr-GyrhbHOlvRScAX0RNsa0T_9eG7xxSwVYug/edit?usp=sharing) by **March 31**

--

4. Determine sampling plan, make changes, and launch survey **April 2**

