---
title: "Newsletter experiment results"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen=999)
```

# load packages
```{r}
library(tidyverse)
library(knitr)
library(DT)
```

# load and tidy data
```{r}
data = read.csv("data/newsletter_data.csv", stringsAsFactors = FALSE) %>%
  mutate_if(is.numeric, ~ ifelse(is.na(.), 999, .)) %>%
  mutate(voting_link = ifelse(request_ballot == 1 | print_form == 1 | request_envelope == 1 | calendar == 1, 1, 0),
         info_involvement_link = ifelse(mailing_list == 1 | pennvotes == 1 | motivote == 1, 1, 0),
         opened_email = ifelse(!opened == 0, 1, 0)) %>%
  mutate_if(is.numeric, ~ ifelse(. == 999, NA, .)) %>%
  gather(var, val, contains("link"), opened_email) %>%
  group_by(group, var) %>%
  mutate(n = n(),
         sum = sum(val, na.rm = TRUE),
         percent = (sum / n) * 100) %>%
  ungroup()

data_sum = read.csv("data/newsletter_data.csv", stringsAsFactors = FALSE) %>%
  mutate_if(is.numeric, ~ ifelse(is.na(.), 999, .)) %>%
  mutate(voting_link = ifelse(request_ballot + print_form + request_envelope + calendar == 1, 1, 0),
         info_involvement_link = ifelse(mailing_list + pennvotes + motivote == 1, 1, 0),
         opened_email = ifelse(!opened == 0, 1, 0)) %>%
  mutate_if(is.numeric, ~ ifelse(. == 999, NA, .)) %>%
  gather(var, val, contains("link"), opened_email) %>%
  group_by(group, var) %>%
  mutate(n = n(),
         sum = sum(val, na.rm = TRUE),
         percent = (sum / n) * 100) %>%
  ungroup()
```

# groupings

`opened_email` = Opened the email

`voting_links` = Clicked on one or more links related to voting behavior

* Request a ballot
* Print request form
* Request envelope
* Check calendar

`info_involvement_links` = Clicked on one or more links to get more information

* Pennvotes.org
* Join the PLTV mailing list
* Join motivote


# summarize the data {.tabset}
Descriptives for each group and action category.

`total n` = total number of people in the group

`action n` = number of people who did this action (e.g. clicking on at least one link in the group)

`action percent` = percent of people who did this action (e.g. clicking on at least one link in the group)

```{r}
data %>%
  select(group, var, n, sum, percent) %>%
  unique() %>%
  mutate(percent = round(percent, 1)) %>%
  rename("action category" = var,
         "total n" = n,
         "action n" = sum,
         "action percent" = percent) %>%
  arrange(`action category`) %>%
  DT::datatable(rownames = FALSE, filter = 'top', extensions = 'FixedColumns', 
                options = list(scrollX = TRUE,
                               scrollY = TRUE,
                               fixedColumns = list(leftColumns = 1)))

```

# visualize {.tabset}
## count {.tabset}
Number of people in each group who opened the email or clicked on at least one link in the category.

```{r, fig.width=12, fig.height=4}
data %>%
  filter(!val == 0) %>%
  ggplot(aes(group, fill = group)) +
  geom_bar(position = position_dodge(.9)) +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 50) +
  facet_grid(~var) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", 4, "continuous")) +
  labs(x = "", y = "count\n") +
  theme_minimal() +
  theme(legend.position = "none")
```

## percent {.tabset}
Percentage of people in each group who opened the email or clicked on at least one link in the category.

```{r, fig.width=12, fig.height=4}
data %>%
  select(group, var, percent) %>%
  unique() %>%
  ggplot(aes(group, percent, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(.9)) +
  geom_text(aes(label = sprintf("%.1f%%", percent)), vjust = 0, nudge_y = 2) +
  facet_grid(~var) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", 4, "continuous")) +
  labs(x = "\nvariable", y = "percentage\n") +
  theme_minimal() +
  theme(legend.position = "none")
```

## percentage of total clicks
Instead of the percentage of people who clicked on at least one link in each category, use the percentage of actual clicks in each category (i.e., the total number of clicks / the total number of link clicks possible)

```{r, fig.width=9, fig.height=4}
data_sum %>%
  select(group, var, percent) %>%
  unique() %>%
  filter(!grepl("open", var)) %>%
  ggplot(aes(group, percent, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(.9)) +
  geom_text(aes(label = sprintf("%.1f%%", percent)), vjust = 0, nudge_y = .03) +
  facet_grid(~var) +
  scale_fill_manual(values = wesanderson::wes_palette("Zissou1", 4, "continuous")) +
  labs(x = "\nvariable", y = "percentage\n") +
  theme_minimal() +
  theme(legend.position = "none")
```

# stats {.tabset}

For all of these models, the differences between the control messages and the experimental messages are not statistically significant, meaning that any observed differences are likely due to chance.

```{r}
fit_mod = function(df) {
  m = glm(val ~ 1 + group, data = df, family = binomial(link = "logit"))
  m_plot = glm(val ~ 0 + group, data = df, family = binomial(link = "logit"))
  plot = sjPlot::plot_model(m_plot, transform = "plogis")
  return(list(m = m, plot = plot))
}

output = data %>%
  mutate(group = factor(group, levels = c("control", "experimental"))) %>%
  group_by(var) %>%
  nest() %>%
  mutate(model = map(data, fit_mod)) %>%
  select(-data) %>%
  unnest() %>%
  bind_cols(type = rep(c("model", "plot"), 3)) %>%
  spread(type, model) %>%
  mutate(tidy_mod = map(model, broom::tidy, conf.int = TRUE)) %>%
  select(-model) %>%
  unnest(tidy_mod) %>%
  mutate(term = gsub("group", "", term),
         term = gsub("\\(Intercept\\)", "Control \\(intercept\\)", term))
```

## opened email {.tabset}
### model
```{r}
var = "opened_email"
output %>% 
  ungroup() %>%
  filter(var == !!var) %>%
  mutate(`logit [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `logit [95% CI]`, p.value) %>%
  kable(digits = 2, format = "pandoc")
```

### plot
```{r}
filter(output, var == !!var)$plot[1]
```

## voting links {.tabset}
### model
```{r}
var = "voting_link"
output %>% 
  ungroup() %>%
  filter(var == !!var) %>%
  mutate(`logit [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `logit [95% CI]`, p.value) %>%
  kable(digits = 2, format = "pandoc")
```

### plot
```{r}
filter(output, var == !!var)$plot[1]
```


## info & involvement links {.tabset}
### model
```{r}
var = "info_involvement_link"
output %>% 
  ungroup() %>%
  filter(var == !!var) %>%
  mutate(`logit [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `logit [95% CI]`, p.value) %>%
  kable(digits = 2, format = "pandoc")
```

### plot
```{r}
filter(output, var == !!var)$plot[1]
```
