---
title: "Week 5: Data visualization"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: true
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = "figs/week4/")

options(scipen = 999)
```


# resources

Here are a number of helpful resources to dig deeper into data visualization with `{ggplot}`:

**UO courses & boot camp modules**

* [Data Visualization Course](https://dataviz-2021.netlify.app/schedule/)
* [Data Visualization with {ggplot}](https://uopsych-r-bootcamp-2020.netlify.app/post/06-ggplot2/)

**Reference guides**

* [`{ggplot}` documentation](https://ggplot2.tidyverse.org/index.html)
* [The R Graph Gallery](https://www.r-graph-gallery.com/)

**Color palettes and themes**

* [Collection of color palettes](https://github.com/EmilHvitfeldt/r-color-palettes)
* [coolers.co color generator](https://coolors.co/)
* [`{ggthemes}`](https://yutannihilation.github.io/allYourFigureAreBelongToUs/ggthemes/)

**Cheat sheets**

* [Data visualization](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf)
* [More useful cheat sheets!](https://www.rstudio.com/resources/cheatsheets/)

# load packages

```{r}
if (!require(pacman)) {
  install.packages("pacman")
}
pacman::p_load("tidyverse", "here", "sysfonts", install = TRUE)
```

# load the data file

Modify the path as needed to where your `week4_data.csv` file is downloaded. Note, my path is a little different, but for you, it should be in the `data/` directory in the same folder as this script.

Import the csv file and assign it to the variable `data`

```{r}
data = read_csv(here("static", "labs", "data", "week4_data.csv"))
```

# tidy the data using code from week 4
In week 4, we did most of these steps independently. Here, we'll use `%>%` to thread the processes together without assigning any intermediate variables.

The key variables we'll be working with today are as follows:

* `behavior_voting`: voted in 2020; single dichotomous item, yes or no
* `CE_attitudes`: civic engagement attitudes; 8-item scale with range 1-7
* `CE_checklist`: checklist of civic engagement activities; 17 dichotonomous items, yes or no
* `pol_eff`: policitical efficacy scale; 4-item scale with range 1-4
* `reasons_yes`: checklist of reasons why people voted in 2020

```{r}
data_tidy = data %>%
  # filter out test and incomplete responses
  filter(!DistributionChannel == "preview") %>%
  filter(Finished == 1 & consent == 1) %>%
  # select a subset of variables 
  select(ResponseId, behavior_voting, reasons_yes,
         starts_with("CE_attitudes"), contains("checklist"), contains("pol_eff")) %>%
  # convert to long format
  pivot_longer(cols = -c(ResponseId, behavior_voting, reasons_yes), names_to = "scale_name") %>%
  # extract item number from scale_name
  extract(col = "scale_name", into = c("scale_name", "item"),
          regex = "(CE_attitudes|CE_checklist|pol_eff)_([0-9]+)") %>%
  # convert responses to numeric and recode response values
  mutate(value = as.numeric(value),
         value = ifelse(test = scale_name == "CE_checklist" & value == 2,
                        yes = 0,
                        no = value),
         behavior_voting = recode(behavior_voting,
                                  "1" = "yes",
                                  "2" = "no")) %>%
  # calculate scale means or sums for each participant
  group_by(ResponseId, scale_name) %>%
  mutate(summarized_value = ifelse(test = scale_name == "CE_checklist", 
                                   yes = sum(value, na.rm = TRUE),
                                   no = mean(value, na.rm = TRUE))) %>%
  # remove the item and value columns
  select(-item, -value) %>%
  # remove repeated observations (rows)
  unique()

```

Let's take a look at the tidied data frame.

We can see that now, instead of multiple items per scale, we have a summary (either a mean or sum) stat in the `summarized_value` column. Now, each participant has one value per scale.

```{r}
data_tidy
```

# check distributions
A good first step when working with data is to visualize the distribution of the variables you're working with. This can help identify outliers or if there are unexpected values.

Let's look at the distributions of `CE_attitudes`, `CE_checklist`, and `pol_eff` 

## histograms {.tabset}
Let's create some histograms using the `geom_histogram()`

### initial plot
```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value)) +
  geom_histogram()
```

### fill 
Use `fill = scale_name` to separate the scales
```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_histogram()
```

### position
Let's make them non-overlapping by using `position = "dodge"`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_histogram(position = "dodge")
```

### facet
Let's separate the scales into 3 separate subplots using `facet_grid(~scale_name)`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_histogram() +
  facet_grid(~scale_name)
```

### bins
Let's change the number of "bins" in the histogram using `bins = 10`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_histogram(bins = 10) +
  facet_grid(~scale_name)
```

## density plots {.tabset}
Rather than plotting a histogram of counts per bin, we'll look at the density using `geom_density()`

### initial plot

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value)) +
  geom_density()
```

### fill 
Use `fill = scale_name` to separate the scales

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_density()
```

### alpha
Change the opacity of the fill color using `alpha = .5`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_density(alpha = .5)
```

### facet 
Separate into subplots using `facet_grid(~scale_name)`

Allow the scale range to differ by specifying `scale = "free"`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_density(alpha = .5) +
  facet_grid(~scale_name, scale = "free")
```

### legend position
Remove the redundant fill legend using `legend.position = "none"`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = scale_name)) +
  geom_density(alpha = .5) +
  facet_grid(~scale_name, scale = "free") +
  theme(legend.position = "none")
```

## density plot by a grouping variable {.tabset}

Now let's see if the distributions differ for people who voted or didn't vote in 2020. 

Because we're plotting each scale separately using `facet_grid(~scale_name)`, we can use `fill` to plot each level of `behavior_voting` separately for each scale.

### initial plot

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = behavior_voting)) +
  geom_density(alpha = .5) +
  facet_grid(~scale_name, scale = "free") +
  theme(legend.position = "top")
```

### color 
Remove the black outlines by specifying `color = NA`

```{r}
data_tidy %>%
  ggplot(aes(x = summarized_value, fill = behavior_voting)) +
  geom_density(alpha = .5, color = NA) +
  facet_grid(~scale_name, scale = "free") +
  theme(legend.position = "top")
```

# summary plots
Now that we've gotten a sense of the distribution, let's look at the average scale scores as a function of voting behavior.

We'll use `stat_summary()` to do this. 

## bar {.tabset}

### initial plot

```{r}
data_tidy %>%
  ggplot(aes(x = behavior_voting, summarized_value)) +
  stat_summary(fun = "mean", geom = "bar") +
  facet_grid(~scale_name)
```

### fill
Let's add some color to distinguish the groups using `fill = behavior_voting`

```{r}
data_tidy %>%
  ggplot(aes(x = behavior_voting, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar") +
  facet_grid(~scale_name) +
  theme(legend.position = "top")
```

### changing x
Let's reduce the redundancy by specifying `x = scale_name` rather than using `facet_grid()`

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar") +
  theme(legend.position = "top")
```

### position
Separate the bars using `position = "dodge"` to push them apart

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  theme(legend.position = "top")
```

### stat_summary
Visualize uncertainty around the means by adding a new `stat_summary()` layer

Visualize the standard error with an error bar with `fun.data = "mean_se"`

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", position = "dodge") +
  theme(legend.position = "top")
```

### 95% CI
Use the 95% confidence interval instead of SE using `fun.data = "mean_cl_boot"`

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = "dodge") +
  theme(legend.position = "top")
```

### width
Change the width of the error bars using `width = 0`
```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = "dodge",
               width = 0) +
  theme(legend.position = "top")
```

### position
Change the position variable so that the erorbars are in the middle of the bars

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun = "mean", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9),
               width = 0) +
  theme(legend.position = "top")
```

## point range {.tabset}
Instead of using bars, let's visualize the means and uncertainty around them using a point range with `geom = "pointrange"`

### initial plot

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, fill = behavior_voting)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange") +
  theme(legend.position = "top")
```

### color
Use color instead of `fill` this time

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, color = behavior_voting)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange") +
  theme(legend.position = "top")
```

### position
Separate the values using `position = position_dodge(.25)`

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, color = behavior_voting)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(.25)) +
  theme(legend.position = "top")
```

### line
Add a line connecting the means by voting behavior group by adding a `stat_summary()` layer

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, color = behavior_voting)) +
  stat_summary(aes(group = behavior_voting), fun = "mean", geom = "line") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(.25)) +
  theme(legend.position = "top")
```

### position
Line things up by changing the line position to match the pointrange position

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, summarized_value, color = behavior_voting)) +
  stat_summary(aes(group = behavior_voting), fun = "mean", geom = "line", 
               position = position_dodge(.25)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(.25)) +
  theme(legend.position = "top")
```

# relationships between continuous variables
Next let's visualize the relationship between two continuous variables using `geom_point()` and `geom_smooth()`

## scatter plots {.tabset}

### initial plot

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist)) +
  geom_point()
```

### trend line
Add a trend line using `geom_smooth()`

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist)) +
  geom_point() +
  geom_smooth()
```

### linear trend
Add a linear trend line by specifying `method = "lm"`

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme(legend.position = "top")
```

## relationship by a grouping variable {.tabset}
As we did previously, let's see if this relationship differs for people who did and didn't vote

Do this using `shape`

### initial plot

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist, shape = behavior_voting)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme(legend.position = "top")
```

### color
Use `color` instead of shape as the aesthetic

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist, color = behavior_voting)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme(legend.position = "top")
```

### fill 
Match the color of the error bands by adding a `fill` aesthetic 

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = CE_checklist, color = behavior_voting,
             fill = behavior_voting)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme(legend.position = "top")
```

# putting it all together
Now that we've gotten our feet wet, we'll focus on creating a publication ready plot to communicate common reasons for voting that Penn students endorse.

First, we'll need to tidy the data and join the text of the reasons from the survey to the data.

## join and tidy data

Check the format of the `reasons_yes` variable

```{r}
data_tidy %>%
  # select relevant variables
  ungroup() %>%
  select(ResponseId, reasons_yes)
```

To replace the numbers with text, first we need to wrangle the data is in the long format and each number selected has its own row.

To do this, we'll do some somewhat complex transformations using `strsplit()`, which creates a list for each value selected, and `unnest()` to convert the lists back to a dataframe.

Then, once the data is in the long format, we can join the text with the corresponding numbers using `left_join()`

```{r}
reason_text = read_csv(here("static", "labs", "data", "week4_data_reasons.csv"))

data_reasons = data_tidy %>%
  # select relevant variables
  ungroup() %>%
  select(ResponseId, reasons_yes) %>%
  # split the selected responses and convert to a single row per response
  mutate(reasons_yes = strsplit(gsub("[][\"]", "", reasons_yes), ",")) %>%
  unnest(reasons_yes) %>%
  # convert to numeric to facilitate joining
  mutate(reasons_yes = as.numeric(reasons_yes)) %>%
  # join with text 
  left_join(., reason_text, by = "reasons_yes") %>%
  # remove missing responses and "other" responses
  filter(!is.na(text) & !text == "Other") %>%
  # get unique responses
  unique()
```

## create plot {.tabset}

Create a bar plot and fancify it

### initial plot

```{r}
data_reasons %>%
  ggplot(aes(x = text)) +
  geom_bar()
```

### flip
Flip the axis using `coord_flip()`

```{r}
data_reasons %>%
  ggplot(aes(x = text)) +
  geom_bar() +
  coord_flip() 
```

### text
Add a count number using `geom_text()`

```{r}
data_reasons %>%
  ggplot(aes(x = text)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10)
```

### label
Remove the flipped x label and add a space between the scale and the flipped y label using "\n"

```{r}
data_reasons %>%
  ggplot(aes(x = text)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount")
```

### Reorder
Reorder the bars based on the count by summarizing the number of responses per text

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n()) %>%
  ggplot(aes(x = reorder(text, n_responses))) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount")
```

### fill
Create grouping categories for different types of reasons and use this variable as the fill aesthetic

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount")
```

### legend position
Move the legend to the bottom of the plot using `legend.position = "bottom"`

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount") +
  theme(legend.position = "bottom")
```

### color
Change the color using `scale_fill_brewer()`

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount") +
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = 1)
```

### color
Change the color by create the variable palette with HEX values

Manually change the color palette using `scale_fill_manual()`

Change the scale name with the `name = "category"` argument

```{r}
palette = c("#1985a1", "#e64626", "#ffb800", "#4c5c68", "#dcdcdd")
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount") +
  theme(legend.position = "bottom") +
  scale_fill_manual(name = "category", values = palette)
```

### theme
Change the theme with `theme_minimal()`, note this must come before any theme layers or it will override them

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_fill_manual(name = "category", values = palette)
```

### title
Add a title by adding a title argument to `labs()`

```{r}
data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount", title = "Reasons for voting in the 2020 election endorsed by Penn students") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_fill_manual(name = "category", values = palette)
```

### title position
Adjust the title position using `plot.title.position = "plot"`

```{r}
# save the plot as plot
(plot = data_reasons %>%
  group_by(text) %>%
  mutate(n_responses = n(),
         category = ifelse(grepl("stake|consequences|financially|future", text), "consequences",
                 ifelse(grepl("bigger|social|community|world|family", text), "prosociality",
                 ifelse(grepl("participate|duty|adult|right", text), "responsibility", 
                 ifelse(grepl("advocate|voice|express", text), "agency", "rebellion/control"))))) %>%
  ggplot(aes(x = reorder(text, n_responses), fill = category)) +
  geom_bar() +
  coord_flip() +
  geom_text(aes(label = stat(count)), stat = "count", nudge_y = 10) +
  labs(x = "", y = "\ncount", title = "Reasons for voting in the 2020 election endorsed by Penn students") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title.position = "plot") +
  scale_fill_manual(name = "category", values = palette))
```

### font {.tabset}
Now that we've got a near final plot, let's learn how to change the font using the `{sysfonts}` package

```{r}
# check what files are installed on your machine
font_files() 

# add a font from google
font_add_google("Roboto")
```

Let's update the font to Helvetica Neue size 14 and convert all grey text to black

```{r}
plot +
  theme(legend.position = "bottom",
        axis.text = element_text(color = "black"),
        text = element_text(size = 14, family = "HelveticaNeue"))
```

### resize
Specify the figure width and height in the chunk options. 

We'll assign this variable as `final_plot` to save it

```{r, fig.width=12, fig.height=6}
(final_plot = plot +
  theme(legend.position = "bottom",
        axis.text = element_text(color = "black"),
        text = element_text(size = 14, family = "HelveticaNeue")))
```

### save the plot
Now that we've got our beautiful plot, let's save it as a png with `ggsave()`

```{r}
ggsave(final_plot, filename = "~/Desktop/plot.png", width = 12, height = 6)
```

# assignment

## other ways to visualize distributions
Check out the types of distribution plots available on [R Graph Gallery](https://www.r-graph-gallery.com/).

Try modifying the following code to use a different distribution geom (e.g. `geom_boxplot` or `geom_violin`)

```{r}
data_tidy %>%
  ggplot(aes(x = scale_name, y = summarized_value))
```

Add the data points to the plot you made by adding a layer with `geom_point()`

```{r}

```

Spread out the data points using `geom_jitter()` instead of `geom_point()`

```{r}

```

Decrease the opacity of the points by adding an alpha argument to `geom_jitter()`

```{r}

```

## scatter plots

Visualize the relationship between `CE_attitudes` and `pol_eff` using `geom_point()` and `geom_smooth()` as we did earlier

```{r}
data_tidy %>%
  spread(scale_name, summarized_value) %>%
  ggplot(aes(x = CE_attitudes, y = pol_eff))
```

Look at this relationship as a function of `behavior_voting` using the color aesthetic

```{r}

```

Move the legend to the top of the plot

```{r}

```


## aesthetics

Change the colors on the plot you just made. 

You can generate your own palettes using [coolers.co](https://coolors.co/) or get some inspiration from [this collection of color palettes in R](https://github.com/EmilHvitfeldt/r-color-palettes)

```{r}

```

Install the `{ggthemes}` package and chose one of the [available themes](https://yutannihilation.github.io/allYourFigureAreBelongToUs/ggthemes/) to add as a layer

```{r}
pacman::p_load("ggthemes", install = TRUE)


```

